Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
paper beautification

The proof above relies on the fact that the relationship between states and next states is defined by
$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
the operation becomes:
\begin{align*}
x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once. We derive the closed form expression for $x_n$

\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
\end{align*}

The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
reference signal so an asymptotically stable system will converge to the origin. We know that the original system
with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
$(A_d  - B_dK)^n*x_0$ must converge to zero.

To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.

A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
\begin{align*}
\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
\end{align*}
Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge

\begin{align*}
x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
\end{align*}

Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.

@@

%\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
%0		& 1 		& 0		\\
%1752	& 0			& -34.07\\
%0		& 0			& -38.27\\
%\end{array}\right]$ & $\left[\begin{array}{c}
%0 \\ 0 \\ 1.923
%\end{array}\right]$ & $\left[\begin{array}{ccc}
%1 & 0 & 0\\
%\end{array}\right]$ & 0 \\ \hline

>>>>

The proof above relies on the fact that the relationship between states and next states is defined by
$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
the operation becomes:
\begin{align*}
x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once. 
We derive the closed form expression for $x_n$ as follows: 
\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
\end{align*}

The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
reference signal so an asymptotically stable system will converge to the origin. We know that the original system
with an infinite-precision controller is stable, because we have synthesized it to meet Jury's criterion. Hence, 
$(A_d  - B_dK)^n*x_0$ must converge to zero.

To show that a fixed-point implementation of the same controller will converge to a finite value, 
we need to show that the infinite sum converges.
A known result is that a power series of matrices converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less than 1, as follows:
%\begin{align*}
$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
%\end{align*}
where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
\begin{align*}
0 + (I - A_d + B_dK)^{-1}B_dk\delta. 
\end{align*}
As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, then the synthesized fixed-point controller results in a safe closed-loop model. 
The convergence to a finite value, however, will not make it asymptomatically stable.

@@

\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
1752	& 0			& -34.07\\
0		& 0			& -38.27\\
0 \\ 0 \\ 1.923
